---
title: "Shiny app pitch"
author: "Vasantha"
date: "22/05/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Summary
- Shiny application is developed for air quality data. 
- Histogram is plotted varible bins that can be chosen by the user using the slider bar. 
- Ozone is plotted against the varible chosen by the user
- Linear regression can be plotted if needed. 
- Finally, ozone levels are predicted for temperature chosen using the slider.
- Main panel is divided as tabs for demonstrating each of the plots.

## Summary of air quality data

```{r}
summary(airquality)
```

## Ozone data

Ozone values are plotted as histogram with number of bins decided by the user by sliding the slider bar.   

```{r, echo = T, message=F, warning=F}
hist(airquality$Ozone, bins = 10)
```

## Plotting ozone vs other environmental parameters
Ozone levels are plotted with respected to other environmental parameters such as temeperaure, solar radiation and wind. Also, a linear regression model is fitted to the model if required. 

```{r, echo = F, message=F, warning=F}
airquality <- na.omit(airquality)
plot(airquality$Wind, airquality$Ozone, xlab = "Wind", ylab = "Ozone")
abline(lm(airquality[,1]~airquality[,3]), col = 'red')
```

## Predict ozone data for differnt temperaure levels
Ozone levels are predicted for the chosen temperaure levels. Assuming the chosen temperature is 100 F, ozone is computed from the fitted model
```{r, echo = F, message=F, warning=F}
model1 <- lm(airquality[,1] ~ airquality[,4])
model1$coefficients[1] + 80 * model1$coefficients[2]
```

## Thank you